The Randomly-Scoped Lambda Calculus

### 2012-12-16 RSLC/paper/paper.tex
Many modern programming languages [cite cite cite cite cite cite]

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathpartir}
\usepackage{url}
\usepackage{graphics}

@@

We define the Randomly-Scoped Lambda Calculus, and show how it can evaluate random natural numbers as well as more popular deterministic functionalities such as factorial and fibonacci.

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathpartir}
\usepackage{url}
\usepackage{graphics}
\usepackage[utopia]{mathdesign}

@@

We define the Randomly-Scoped Lambda Calculus, and show how it can be used to compute random natural numbers, while also providing more popular deterministic functionalities such as factorial and fibonacci.

@@

Many modern programming languages~\cite{python,lambda,sml,GoLang,RustLang,mla,haskell98,patenttroll,wikiplia}
